### 2018-03-26 Graduate - Introduction to Analysis II/HW5/5HW20180313.tex
finish hw 5

>>>>

First, it is trivial that $H(G)$ is a commutative group under addition. Besides, if $f, g\in H(G)$, then $fg$ is also analytic, $fg = gf$, and $(fg)h = f(gh)$. Hence $H(G)$ is a commutative ring. If there is a zeros divisor $f\ne 0$, then there is $g\ne 0\in H(G)$, s.t. $fg = 0$. Let $\{z_i\}$ be zeros of $f$, then since $f$ is analytic, the zeros are isolated, which means if there are at most countable number of zeros in $G$, otherwise there is a limit point of zeros, which against the property of analytic functions. It is the same for $g$, hence $fg = 0$ only at countable number of points in $G$, which makes a contradiction.

With the same arguments, we can show $M(G)$ is a commutative ring with 0 and 1, which are $f\equiv 0$ and $f\equiv 1$. Let $f\in M(G)$, and we only need to show that $\frac{1}{f}\in M(G)$. In fact, if $f\in M(G)$, then $f$ has countable number of zeros, hence $\frac{1}{f}$ has countable number of poles, and the order of each pole is finite. Hence $\frac{1}{f}\in M(G)$.
